A Minimal Book Example

### 2020-02-13 manuscript/test/04-simulation.Rmd
remove thesisdown files, update notes

---
title: "My first simulation"
author: "Gerbrich Ferdinands"
date: "2/7/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

![]("figs/myfirstsim/Figure_1.png")

@@

![]("figs/myfirstsim/Figure_2.png")

@@

![when _z_ goes up, optimized parameters perform better.]("figs/myfirstsim/Figure_3.png")

@@

![]("figs/myfirstsim/computation.png")

2191 was best performing with a loss of 0.1124

![]("figs/myfirstsim/optmizationresult.png")

>>>>

# My first simulation
```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

```{r}
knitr::include_graphics("figs/myfirstsim/Figure_1.png")
```

@@

```{r}
knitr::include_graphics("figs/myfirstsim/Figure_2.png")
```

@@

```{r}
knitr::include_graphics("figs/myfirstsim/Figure_3.png")
```

@@

```{r}
knitr::include_graphics("figs/myfirstsim/computation.png")
```
2191 was best performing with a loss of 0.1124

```{r}
knitr::include_graphics("figs/myfirstsim/optmizationresult.png")
```
